Symmetric Circuits for Rank Gates

### 2018-03-04 sections/background.tex
I have made changes to the section "symmetric circuits" and updated every other section in line with changes made.

\subsection{Boolean Functions, Bases, and Circuits}
A \emph{Boolean function} is a function of the form $f: \{0,1\}^X \rightarrow
\{0,1\}$, for some finite index set $X$. We call a Boolean function $f:
\{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma \in \sym_X$
and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It follows that
a Boolean function is symmetric if, and only if, the output of the function is
entirely determined by the number of ones in the input. We say a function $f :
\{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if its restriction to
inputs of size $n$ is symmetric for all $n$.

A \emph{Boolean basis} (or \emph{basis}) is a set of Boolean functions. We
always denote a basis by $\BB$. It is common in the literature to define a basis
using a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^* \rightarrow
\{0,1\}$. We write $\BB = \{f_1, \ldots, f_k\}$ to denote the basis consisting
of all Boolean functions $f^n_i : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in
\nats$, $i \in [k]$, and $f^n_i$ is the restriction of $f_i$ to strings of
length $n$. We have $\AND, \OR, \NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$,
where $\AND, \OR, \NAND$ are the usual (unbounded fan-in) logical operators, and
$\MAJ$ is the majority function. We write $\BS := \{\AND, \OR, \NOT\}$ to denote
the \emph{standard basis} and $\BM := \BS \cup \{\MAJ\}$ to denote the
\emph{majority basis}.

>>>>

\subsection{Boolean Functions, Bases, and Circuits}
A (finite) \emph{Boolean function} is a function of the form $f: \{0,1\}^X
\rightarrow \{0,1\}$, for some finite index set $X$. We call a Boolean function
$f: \{0,1\}^X \rightarrow \{0,1\}$ \emph{symmetric} if for all $\sigma \in
\sym_X$ and $\vec{a} \in \{0,1\}^X$, $f (\vec{a} \sigma) = f(\vec{a})$. It
follows that a Boolean function is symmetric if, and only if, the output of the
function is entirely determined by the number of ones in the input. We say a
Boolean function $f : \{0,1\}^{*} \rightarrow \{0,1\}$ is \emph{symmetric} if
its restriction to inputs of size $n$ is symmetric for all $n$.

We depart slight from the conventional notion of a basis in this paper. We
define a \emph{Boolean basis} (or \emph{basis}) to be a set of finite Boolean
functions. We always denote a basis by $\BB$. It is common in the literature to
define a basis as a finite sequence of functions $f_1, \ldots , f_k:\{0,1\}^*
\rightarrow \{0,1\}$. In this paper we instead think of this sequence as
\emph{generating} a basis, and write $\BB = \langle f_1, \ldots, f_k \rangle$ to
denote the basis generated by these functions, i.e.\ $\BB$ consists of all the
Boolean functions $f_i[n] : \{0,1\}^n \rightarrow \{0,1\}$ where $n \in \nats$,
$i \in [k]$, and $f_i[n]$ is the restriction of $f_i$ to strings of length $n$.
In other words $\langle f_1, \ldots , f_k \rangle$ is the union of $\{f_i[n] : n
\in \nats\}$ for each $f_i$ in the generating sequence. We have $\AND, \OR,
\NAND, \MAJ : \{0,1\}^* \rightarrow \{0,1\}$, where $\AND, \OR, \NAND$ are the
usual (unbounded fan-in) logical operators, and $\MAJ$ is the majority function
(i.e.\ the function that outputs one if more than half of bits in the inputs are
one). We write $\BS := \langle \AND, \OR, \NAND\} \rangle$ to denote the
\emph{standard basis} and $\BM := \langle \AND, \OR, \NAND , \MAJ \rangle$ to
denote the \emph{majority basis}.
